The development of infants' responses to mispronunciations: A Meta-Analysis

### 2020-02-03 VonHolzenBergmann_MPMetaAnalysis.Rmd
implementing finalization comments

In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g. cat-hat). Twenty years worth of studies have examined infants' application of phonological categories during word recognition through the mispronunciation sensitivity paradigm to probe this latter distinction. At the turn of the millennium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream [@Jusczyk1995] and learning minimal pairs [@Stager1997]. @Swingley2000 expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition. American-English learning 18- to 23-month-olds were presented with pairs of images (e.g. a baby and a dog) and their eye movements to each image were recorded. Infants either heard the correct label (e.g. "baby") or a mispronounced label (e.g. "vaby") for one of the images. Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looks to the target image than mispronounced labels. @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.

Why should sensitivity to mispronunciations pose a challenge to the young infant? Critically, the native language being learned determines the relevant contrasts for the infant language-learner. For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish. These contrasts are therefore not innate, but must be learned. As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired. The time is thus ripe to aggregate all publicly available evidence using a meta-analysis to assess infants' developing ability to correclty apply the phonological distinctions for their native language during word recognition. In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for a notable exception). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

@@

An *increase* in mispronunciation sensitivity is predicted by a maturation in phono-lexical representations from holistic to more detailed and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010]. More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop. The first words that infants learn are often not similar sounding [e.g. mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary. With time, more phonologically similar words are learned, which may drive a need to the infant to represent familiar words with more fine phonological detail. A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980]. This argument is supported by the results of @Mani2010kepstups. Here, 12-month-old infants were divided into low and high vocabulary groups. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Consequently, if increasing age and/or vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship with mispronunciation sensitivity.

Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship [@Swingley2000; @Swingley2002; @Swingley2009; @Zesiger2012; @Mani2008; @Bailey2002; @Mani2007; @Ballem2005]. Furthermore, other studies testing more than one age have found *no difference* in mispronunciation sensitivity [@Swingley2000; @Bailey2002; @Zesiger2012]. Such evidence supports an early specificity hypothesis, which suggests continuity in how infants' represent familiar words. According to this account, infants represent words with phonological detail already at the onset of lexical acquisition and that this persists throughout development.

There are no theoretical accounts that would predict decreased *mispronunciation sensitivity*, but at least one study has found a *decrease* in sensitivity to small mispronunciations . @Mani2011 tested 18- and 24-month-olds' sensitivity to increasingly larger mispronunciations (1-, 2-, and 3-feature phonological changes). Although both groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to 1-feature mispronunciations. To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below). In contrast, 18-month-olds did not show graded sensitvity, showing similar disruptions to word recognition for smaller and larger mispronunciations.

To disentangle the predictions that phonological representations are progressively specified or specified early, we investigate the relationship between mispronunciation sensitivity and both age as well as vocabulary size. But, this may not account for all variability found in the literature. Although all mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the position of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image. These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete.

@@

The manipulations that might increase task demands, such as overlap between target and distractor, are also theoretically interesting, focusing on issues at the intersection of phonological development and lexical processing. For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up exploratory analyses. We outline first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.

The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations. Some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e. 1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] feature changes. This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity.

Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016], known as the consonant bias. A learned account predicts that a C-bias emerges over development [@Floccia2014; @Nazzi2016; @Keidel2007] and that this emergence is impacted by the language family of the infants' native language [@Nazzi2016]. In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen]. One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016]. In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to determine whether infants exhibit more sensitivity to consonant compared to vowel mispronunciations of familiar words.

Models of spoken word processing place more or less importance on the position of a phoneme in a word. The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word. In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations. The *position of mispronunciation* in the word may therefore differentially interrupt the infant's word recognition process, with onset mispronunciations leading to greater mispronunciation sensitivity than medial or coda mispronunciations.

A second question is whether the context modulates infants' responses to mispronunciations. In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a vowel mispronunciation of the target word "doggie", the image of a dog would be paired with a distractor image that shares onset overlap, such as "doll". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Swingley1999]. Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change. Note that in this case, the mispronunciation is necessarily either word-medial or –final, thus possibly creating an interaction between mispronunciation position and phonological overlap.

Most studies present infants with pictures of two known objects, thus ruling out the unlabeled competitor, or distractor, as possible target. It is thus not surprising that infants tend to look towards the target more, even when its label is mispronounced. In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016]. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003]. This ability is developing from 18 to 30 months [@Bion2013] and we may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar. This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared.

Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table \@ref(tab:SummaryTable)). Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare. Indeed, the majority of studies focus on infants learning English as a native language and a sufficient sample of other languages is therefore lacking. Although we do not explicitly compare overall mispronunciation sensitivity by language (although we examine consonant and vowel mispronunciation sensitivity by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.

In sum, the studies we have reviewed begin to paint a picture of the development of infants' use of phonological detail in familiar word recognition. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early phono-lexical development. Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciation sensitivity. Because we aggregate data over various age groups, this meta-analysis can investigate the role of maturation by assessing the impact of age and vocabulary size. We also explore the influence of different linguistic (mispronunciation size, position, and type) and contextual (overlap between target and distractor labels; distractor familiarity) factors on the study of mispronunciation sensitivity. Finally, we explore potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].

@@

Sum_table$dist_overlap <- ifelse(grepl("onset", Sum_table$dist_overlap), gsub("onset", "O", Sum_table$dist_overlap), Sum_table$dist_overlap)
Sum_table$dist_overlap <- ifelse(grepl("medial", Sum_table$dist_overlap), gsub("medial", "M", Sum_table$dist_overlap), Sum_table$dist_overlap)
Sum_table$dist_overlap <- ifelse(grepl("coda", Sum_table$dist_overlap), gsub("coda", "C", Sum_table$dist_overlap), Sum_table$dist_overlap)

@@

apa_table(Sum_table, col.names = c("Paper", "Format", "Age", "Vocabulary", "Familiarity", "Target Overlap", "Size", "Position", "Type", "N Effect Sizes"), caption = "Summary of all studies. Age: truncation of mean age reported in the paper. Vocabulary: Comp = comprehension, Prod = production. Distractor Familiarity: Fam = Familiar Distractor, Unfam = Unfamiliar Distractor. Distractor Target Overlap: position of overlap between target and distractor; O = onset, M = medial, C = coda. Mispronunciation Size: number of features changed; commas indicate when sizes were compared separately (e.g. 1, 2, 3), dashes indicate the range of sizes were aggregated (e.g. 1-3). Mispronunciation Position: O = onset, M = medial, C = coda. Mispronunciation Type: C = consonant, V = vowel, T = tone. For both Mispronunciation Position and Type, a slash separator indicates that is was tested but a distinction was not made in the stimuli. For all categories, unspec. indicates that the value was unspecified in the paper", landscape = TRUE, font_size = "scriptsize", col_spanners = list(`Distractor` = c(5, 6), `Mispronunciation` = c(7, 9)))

@@

1. Condition: Were words mispronounced or not;  
2. Mean age reported per group of infants, in days;  
3. Vocabulary size, measured by a standardized questionnaire or list;
4. Position of mispronunciation: onset, medial, offset, or mixed;
5. Size of mispronunciation, measured in features changed;
6. Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word; 
7. Type of mispronunciation: consonant, vowel, or both.
8. Distractor familiarity: familiar or unfamiliar;

@@

To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor]. We use a multilevel random effects model which estimates the mean and variance of effect sizes sampled from an assumed distribution of effect sizes. In the random effect structure we take into account the shared variance of effect sizes drawn from the same paper, and nested therein that the same infants might contribute to multiple effect sizes.

@@

The stronger publication bias for correct pronunciation might reflect the status of this condition as a control. If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into question. However, even in a well-powered study one would expect the regular occurrence of null results even though as a population infants would reliably show the expected object identification effect.

@@

The studies examined in this meta-analysis examined mispronunciation sensitivity, but many also included more specific questions aimed at uncovering more detailed phonological processes at play during word recognition. Not only are these questions theoretically interesting, they also have the potential to change the difficulty of a msipronunciation sensitivity experiment. It is possible that the lack of developmental change in mispronunciation sensitivity found by our meta-analysis does not capture a true lack of change, but is instead influenced by differences in the types of tasks given to infants of different ages. If infants' word recognition skills are generally thought to improve with age and vocabulary size, research questions that tap more complex processes may be more likely to be investigated in older infants. In the following section, we investigate the role that different moderators play in mispronunciation sensitivity. To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.

@@

p.MS <- ggplot(dat.f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_violin() + 
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Hedges' g")

@@

ms.agg <- ggplot(dat.cm, aes(location_label, Misp_sensitivity, fill = location_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

@@

ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

@@

ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
  facet_grid(.~lang_family)+
    geom_violin() + 
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Hedges' g")

@@

When language family was included as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`. The three-way interaction between mispronunciation type, condition, language family was large and also significant , $\beta$`r full_estimate(sum_eff_famcv)`. As can be seen in Figure \@ref(fig:PlotCVEffectLang)a, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages. Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.

@@

>>>>

In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g. cat-hat). Twenty years' worth of studies have examined infants' application of phonological category knowledge during word recognition through the mispronunciation sensitivity paradigm to probe the development of this latter distinction. At this point, a picture on the functional use of language-specific phonetic and phonological knowledge began to emerge. At the turn of the millennium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream [@Jusczyk1995] and learning minimal pairs [@Stager1997]. Both studies and the lines of research they sparked showed that under the right conditions, even young infants can use their emerging native language phonological skills during word-level language processing.

@Swingley2000 expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition. American-English learning 18- to 23-month-olds were presented with pairs of images of words they were very likely to know (e.g. a baby and a dog) and their eye movements to each image were recorded. Infants either heard the correct label (e.g. "baby") or a mispronounced label (e.g. "vaby") for one of the images. Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looks to the target image than mispronounced labels. @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.

Why should sensitivity to mispronunciations pose a challenge to the young infant and thus the findings of @Swingley2000 be found novel? There are two key challenges the infant learner has to contend with. First, the native language being learned determines the relevant contrasts for the infant language-learner. These contrasts are therefore not innate, but must be learned. For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish. Second, across talkers, these sounds might be realized differently, and change even as the talker talks to an infant or adult [e.g. @Benders2013]. As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired and applied to lexical representations. The time is thus ripe to aggregate all publicly available evidence using a meta-analysis. In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for notable exceptions). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

@@

An *increase* in mispronunciation sensitivity is predicted by a maturation in phono-lexical representations from holistic to more detailed and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010]. More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop. The first words that infants learn are often not similar sounding [e.g. mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary. **According to PRIMIR [@Curtin2011; @Curtin2007; @Werker2005] infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.** A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980]. This argument is supported by the results of @Mani2010kepstups. Here, 12-month-old infants were divided into low and high vocabulary groups. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations (see below for further discussion on consonant-vowel assymmetry). If increasing age and/or vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship of either with mispronunciation sensitivity.

Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship [@Swingley2000; @Swingley2002; @Swingley2009; @Zesiger2012; @Mani2008; @Bailey2002; @Mani2007; @Ballem2005]. Furthermore, other studies testing more than one age have found *no difference* in mispronunciation sensitivity [@Swingley2000; @Bailey2002; @Zesiger2012]. Such evidence supports an early specificity hypothesis, which suggests continuity in how infants represent familiar words. According to this account, infants represent words with phonological detail already at the onset of lexical acquisition and that this persists throughout development.

There are no theoretical accounts that would predict *decreased* mispronunciation sensitivity, but at least one study has found a decrease in sensitivity to small mispronunciations . @Mani2011 tested 18- and 24-month-olds' sensitivity to increasingly larger mispronunciations: 1- (bed-bud), 2- (foot-fit), and 3-feature phonological changes (doll-deal). Although both age groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to more subtle 1-feature mispronunciations. To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below). In contrast, 18-month-olds did not show graded sensitivity, showing similar disruptions to word recognition for smaller and larger mispronunciations.

To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size. But, this may not account for all variability found in the literature. Although infant mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the location of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image. These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. We thus follow our analyses of a developmental trajectory with one of features of the task, and line out here task effects which can shed further light on early phono-lexical representations and their maturation.

@@

The manipulations that might increase task demands, such as overlap between target and distractor, are also theoretically interesting, focusing on issues at the intersection of phonological development and lexical processing. For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up analyses. We outline first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.

The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations. Some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e. 1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] feature changes. This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity [@Bailey2005]

Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016], known as the consonant bias. A learned account predicts that a consonant bias emerges over development [@Floccia2014; @Nazzi2016; @Keidel2007] and that this emergence is impacted by the language family of the infants' native language [@Nazzi2016]. In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen] and do not compare infants learning different native languages [for evidence from word-learning see @Floccia2014; @Nazzi2009a]. One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016]. In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to assess the predictions of the learned account of the consonant bias.

The *position of mispronunciation* in the word may differentially interrupt the infant's word recognition process, with onset mispronunciations leading to greater mispronunciation sensitivity than medial or coda mispronunciations. Models of spoken word processing place more or less importance on the position of a phoneme in a word. The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word. In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.

A second set of questions is whether the context modulates infants' responses to mispronunciations. In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a vowel mispronunciation of the target word "doggie", the image of a dog would be paired with a distractor image that shares onset overlap, such as "doll". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Swingley1999]. Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change. Note that in this case, the mispronunciation is necessarily either word-medial or –final, thus possibly creating an interaction between mispronunciation position and phonological overlap.

We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar. This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared. Most studies present infants with pictures of two known objects, thereby ruling out the unlabeled competitor, or distractor, as possible target. It is thus not surprising that infants tend to look towards the target more, even when its label is mispronounced. In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016]. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003], an ability that is developing from 18 to 30 months [@Bion2013].

In sum, the studies we have reviewed begin to paint a picture of the development of infants' use of phonological detail in familiar word recognition. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early phono-lexical development. Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciation sensitivity. Because we aggregate data over  age groups, this meta-analysis can investigate the role of maturation by assessing the impact of age, and when possible vocabulary size. We also test the influence of different linguistic (mispronunciation size, position, and type) and contextual (overlap between target and distractor labels; distractor familiarity) factors on the study of mispronunciation sensitivity. Finally, we explore potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].

@@

Sum_table$dist_overlap <- ifelse(grepl("onset", Sum_table$dist_overlap), gsub("onset", "O", Sum_table$dist_overlap), Sum_table$dist_overlap)
Sum_table$dist_overlap <- ifelse(grepl("medial", Sum_table$dist_overlap), gsub("medial", "M", Sum_table$dist_overlap), Sum_table$dist_overlap)
Sum_table$dist_overlap <- ifelse(grepl("coda", Sum_table$dist_overlap), gsub("coda", "C", Sum_table$dist_overlap), Sum_table$dist_overlap)
Sum_table$dist_overlap <- ifelse(grepl("novel", Sum_table$dist_overlap), gsub("novel", "unfam", Sum_table$dist_overlap), Sum_table$dist_overlap)

@@

apa_table(Sum_table, col.names = c("Paper", "Format", "Age", "Vocabulary", "Familiarity", "Target Overlap", "Size", "Position", "Type", "N Effect Sizes"), caption = "Summary of all studies. Age: mean age(s) reported in the paper (in months). Vocabulary: Comp = comprehension, Prod = production. Distractor Familiarity: Fam = Familiar Distractor, Unfam = Unfamiliar Distractor. Target Overlap: position of overlap between target and distractor; O = onset, M = medial, C = coda. Mispronunciation Size: number of features changed; commas indicate when sizes were compared separately (e.g. 1, 2, 3), dashes indicate the range of sizes were aggregated (e.g. 1-3). Mispronunciation Position: O = onset, M = medial, C = coda. Mispronunciation Type: C = consonant, V = vowel, T = tone. For both Mispronunciation Position and Type, a slash separator indicates that is was tested but a distinction was not made in the stimuli. For all categories, unspec. indicates that the value was unspecified in the paper", landscape = TRUE, font_size = "scriptsize", col_spanners = list(`Distractor` = c(5, 6), `Mispronunciation` = c(7, 9)))

@@

1. Condition: Were words mispronounced or not;
2. Mean age reported per group of infants, in days; 
3. Vocabulary size, measured by a standardized questionnaire or list;
4. Position of mispronunciation: onset, medial, offset, or mixed;
5. Size of mispronunciation, measured in features changed;
6. Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
7. Type of mispronunciation: consonant, vowel, or both;
8. Distractor familiarity: familiar or unfamiliar;

@@

To consider the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor]. We use a multilevel random effects model which estimates the mean and variance of effect sizes sampled from an assumed distribution of effect sizes. In the random effect structure we take into account the shared variance of effect sizes drawn from the same paper, and nested therein that the same infants might contribute to multiple effect sizes.

@@

The stronger publication bias for correct pronunciation might reflect the status of this condition as a control. If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into question. However, even in a well-powered study one would expect the regular occurrence of null results even though as a population, infants would reliably show the expected object identification effect.

@@

The studies examined in this meta-analysis examined mispronunciation sensitivity, but many also included more specific questions aimed at uncovering more detailed phonological processes at play during word recognition. Not only are these questions theoretically interesting, they also have the potential to change the difficulty of a mispronunciation sensitivity experiment. It is possible that the lack of developmental change in mispronunciation sensitivity found by our meta-analysis does not capture a true lack of change, but is instead influenced by differences in the types of tasks given to infants of different ages. If infants' word recognition skills are generally thought to improve with age and vocabulary size, research questions that tap more complex processes may be more likely to be investigated in older infants. In the following section, we investigate the role that different moderators play in mispronunciation sensitivity. To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.

@@

p.MS <- ggplot(dat.f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_violin() + 
  geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Hedges' g")

@@

ms.agg <- ggplot(dat.cm, aes(location_label, Misp_sensitivity, fill = location_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

@@

ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

@@

ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
  facet_grid(.~lang_family)+
    geom_violin() + 
  geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Hedges' g")

@@

When language family was included as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`. The three-way interaction between mispronunciation type, condition, language family was large and also significant, $\beta$`r full_estimate(sum_eff_famcv)`. As can be seen in Figure \@ref(fig:PlotCVEffectLang)a, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages. Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.

@@

ptt_power <- round(ptt$power*100, 0)
